---
title: "Broken Window"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css}
d-title, d-byline {
  display: none
}
```

<div style="margin-top:20px; margin-bottom: 0px;" id="instructions">

## Instructions: Free speech samples

```{r panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

::::: {.panelset}

::: {.panel}

## A. STROKE STORY and COPING {.panel-name}

1. **"I’m going to be asking you to do some talking. How do you think your speech is these days?"**

  *If no response in approximately 10 seconds, prompt:*\
  - **"How's your talking?"**

  *Listen, encourage full response.*

  *If no response, use Troubleshooting questions.*
  
2. **"Do you remember when you had your stroke?"**

  *If yes,* **"Please tell me about it."**

  *If no,* **"Well, how about your first memories after the stroke. What can you tell me about that?"**
 
  *If no response in approximately 10 seconds, prompt:*\
  - **"Try to tell me about the day you had your stroke."**

  *Listen, encourage full response.*

  *If no response, use Troubleshooting questions.*

At a natural juncture add:

3. **"Tell me about your recovery. What kinds of things have you done to try to get better since your stroke?"**

  *If no response in approximately 10 seconds, prompt:*\
  - **"Tell me about any changes you’ve needed to make in your daily life."**
  
  *If no response, use Troubleshooting questions.*

**"Now I’m going to ask you to do a few more things where you need to talk. Please talk as much as you can about each one, because we’re really interested in knowing about your language."**

:::

::: {.panel}

## B. IMPORTANT EVENT {.panel-name}

**"Thinking back, can you tell me a story about something important that happened to you in your life? It could be happy or sad or from any time -- from when you were a kid or more recently."**

*If no response in approximately 10 seconds, prompt:*\
  - **"For instance, you could tell me about a trip you took or something about your family or your work -- anything."**

*If no response, use Troubleshooting questions.*

:::

:::::

